\plaintitle

### 2016-09-16 drafts/labor/introduction.tex
most notes on piecework_lit; will finish up tomorrow!
typo in intro

\topic{The extant body of work has ostensibly sought to answer one underlying question:
What does the future hold for crowd work and those that do it?}
Researchers have offered their input on this open question along three major threads:
\begin{enumerate}
  \item \nameref{sec:complexity}?
        Specifically,
        \begin{inlinelist}
          \item how complex are the goals that crowd work can accomplish? and
          \item how far will crowd work reach into the everyday lives of people?
          \msb{which people? workers? requesters? do you mean, will recruiting crowd work be the domain of experts or everyday end users?}
          \ali{I think I'm trying to ask how much of the world will do crowd work --- the whole world, or just representative slices of lots of different types of people (experts, non--experts, etc\dots)}
        \end{inlinelist}
        \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,
              Nebeling:2016:WCW:2858036.2858169,
              Hahn:2016:KAB:2858036.2858364};
  \item \nameref{sec:decomposition}?
  % To what extent can we decompose work (especially into micro--tasks)? \msb{How far can work be decomposed into smaller and smaller microtasks?}
        \cite{embracingErrorKrishna,bernsteinSoylent,sensitiveTasks,
              LykourentzouPersonalityMatters,KucherbaevReLauncher,
              Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
              Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item \nameref{sec:relationships}?
        \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,
              whyWouldAnyoneBrewer,takingAHITMcInnis}
        % \ali{is this about collective action? yes; also, career growth? education? governance? sociality? wages?}
\end{enumerate}

\subsection{Piecework as a lens to understand crowdsourcing}
This large and growing body of research has conversed
to varying degrees with labor scholarship,
but has not offered a persuasive framing for holistically explaining
the developments in worker processes that researchers have developer, or
the phenomena in social environments we have observed;
nor has any research, to our knowledge,
gone as far as predict future developments.
To the extent that the research community has explored the boundaries of crowd work,
it nevertheless has not reflected on the underlying mechanisms determining those boundaries.
Similarly, work directed toward the decomposition of tasks has begun to appreciate the limits of decomposition,
but on the whole it hasn't considered the relationship between the decomposition of work and the complexity of work.
% \ali{Mixed feelings about this because I think I'll need to go back into decomposition and
% give a whole thing on \citeauthor{marx2012economic}
% if I bring this up as a real failing of the crowd work research to date.
% Thoughts?}
While researchers are quickly picking up on the importance of
the relationships between workers in these platforms,
this research seems to be unfolding without the benefit of any of
the inter--personal labor research that has been informing modern work for the better part of a century.
% \ali{Overall: too long? too vague? overstating the shortcomings?}

>>>>

\topic{The extant body of work has ostensibly sought to answer one underlying question:
What does the future hold for crowd work and those that do it?}
Researchers have offered their input on this open question along three major threads:
\begin{enumerate}
  \item \nameref{sec:complexity}?
        Specifically,
        \begin{inlinelist}
          \item how complex are the goals that crowd work can accomplish? and
          \item how far will crowd work reach into the everyday lives of people?
          \msb{which people? workers? requesters? do you mean, will recruiting crowd work be the domain of experts or everyday end users?}
          \ali{I think I'm trying to ask how much of the world will do crowd work --- the whole world, or just representative slices of lots of different types of people (experts, non--experts, etc\dots)}
        \end{inlinelist}
        \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,
              Nebeling:2016:WCW:2858036.2858169,
              Hahn:2016:KAB:2858036.2858364};
  \item \nameref{sec:decomposition}?
        \cite{embracingErrorKrishna,bernsteinSoylent,sensitiveTasks,
              LykourentzouPersonalityMatters,KucherbaevReLauncher,
              Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
              Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item \nameref{sec:relationships}?
        \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,
              whyWouldAnyoneBrewer,takingAHITMcInnis}
        % \ali{is this about collective action? yes; also, career growth? education? governance? sociality? wages?}
\end{enumerate}

\subsection{Piecework as a lens to understand crowdsourcing}
This large and growing body of research has conversed
to varying degrees with labor scholarship,
but has not offered a persuasive framing for holistically explaining
the developments in worker processes that researchers have developed, or
the phenomena in social environments we have observed;
nor has any research, to our knowledge,
gone as far as predict future developments.
To the extent that the research community has explored the boundaries of crowd work,
it nevertheless has not reflected on the underlying mechanisms determining those boundaries.
Similarly, work directed toward the decomposition of tasks has begun to appreciate the limits of decomposition,
but on the whole it hasn't considered the relationship between the decomposition of work and the complexity of work.
% \ali{Mixed feelings about this because I think I'll need to go back into decomposition and
% give a whole thing on \citeauthor{marx2012economic}
% if I bring this up as a real failing of the crowd work research to date.
% Thoughts?}
While researchers are quickly picking up on the importance of
the relationships between workers in these platforms,
this research seems to be unfolding without the benefit of any of
the inter--personal labor research that has been informing modern work for the better part of a century.
% \ali{Overall: too long? too vague? overstating the shortcomings?}
